Road Segment Prioritization for Bicycle Infrastructure

### 2020-10-30 README.Rmd
Update paper, show Figure of growth in readme

---
title: Road Segment Prioritization for Bicycle Infrastructure
date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography: mybibfile.bib
#linenumbers: true
numbersections: true
#output: rticles::elsevier_article
output:
  # bookdown::github_document2
  bookdown::pdf_document2
---

@@

<!-- \begin{figure} [h!] -->

@@

<!--   \includegraphics[width=1\linewidth]{../../data/Manchester/Plots/Growth_Results/growth_existing_infra_satisfied_km_all_flow_column.png} -->

@@

<!--   \includegraphics[width=1\linewidth]{../../data/Manchester/Plots/Growth_Results/growth_community_4_satisfied_km_all_flow_column.png} -->

>>>>

---
title: Road Segment Prioritization for Bicycle Infrastructure
date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography: mybibfile.bib
#linenumbers: true
numbersections: true
#output: rticles::elsevier_article
output:
  bookdown::github_document2
  # bookdown::pdf_document2:
  #   extra_dependencies: ["subcaption", "longtable"]
---

@@

```{r growth, fig.cap="teswt", out.width="48%", fig.show='hold'}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_existing_infra_satisfied_km_all_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_community_4_satisfied_km_all_flow_column.png"
))
```

<!-- Todo: uncomment for final submission -->
<!-- \begin{figure} [h!] -->

@@

<!--   \includegraphics[width=1\linewidth]{data/Manchester/Plots/Growth_Results/growth_existing_infra_satisfied_km_all_flow_column.png} -->

@@

<!--   \includegraphics[width=1\linewidth]{data/Manchester/Plots/Growth_Results/growth_community_4_satisfied_km_all_flow_column.png} -->
